---
output: html_document
---
---
title: "DSC-RTP National Database Dashboard"
author: "Robert P. McGuinn"
date: "February 3, 2015"
output: html_document
--- 
##### Database Version: DSCRTP_NatDB_20141219-0.txt

***

```{r load_data_and_packages, echo=FALSE, message=FALSE, warning=FALSE}
load("C:/rworking/DeepSeaData20150128/data.noflag.RData")
data <- data
library(dplyr)
library(knitr)
library(ggplot2)

#define unflagged dataset
data_unfl<-
  data %>%
  filter(Flag == 0)

data_flagged<-
  data %>%
  filter(Flag == 1)
```

***

# Global Summary
* Total number of records in the database (flagged + unflagged, global): **`r length(data$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_Global, echo=FALSE, results='hide'}
x <- (length(data_flagged$CatalogNumber)/length(data$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(x, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data$ScientificName))`**

***
##### Table of the number of database records (n) contributed by each Data Provider: 
``` {r DataProvider_Global, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory: 
``` {r VerNacularName_Pie_Global, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank: 
``` {r TaxonRank_Pie_Global, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges: 
``` {r Coral_v_Sponge_Pie_Global, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records:
``` {r Depth_Summary_Global, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth
``` {r Depth_Summary_Boxplots_Global, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Class,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Class", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution   
``` {r Depth_Histogram_Global, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation:
``` {r gisLME_Global, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory: 
``` {r DataProvider-VernacularNameCategory_Global, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

***

***

# Pacific Region  
``` {r sub_Pacific, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisPacificFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "Pacific"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_Pacific, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_Pacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_Pacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_Pacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_Pacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_Pacific, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_Pacific, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_Pacific, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_Pacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_Pacific, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_Pacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_Pacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

***

***

# Western Pacific Region  
``` {r sub_WesternPacific, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisWesternPacificFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "WesternPacific"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_WesternPacific, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_WesternPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_WesternPacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_WesternPacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_WesternPacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_WesternPacific, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_WesternPacific, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_WesternPacific, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_WesternPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_WesternPacific, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_WesternPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_WesternPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

***

# North Pacific Region  
``` {r sub_NorthPacific, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisNorthPacificFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "NorthPacific"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_NorthPacific, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_NorthPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_NorthPacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_NorthPacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_NorthPacific, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_NorthPacific, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_NorthPacific, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_NorthPacific, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_NorthPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_NorthPacific, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_NorthPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_NorthPacific, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

***

# Gulf of Mexico Region  
``` {r sub_GulfofMexico, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisGulfofMexicoFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "GulfofMexico"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_GulfofMexico, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_GulfofMexico, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_GulfofMexico, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_GulfofMexico, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_GulfofMexico, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_GulfofMexico, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_GulfofMexico, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_GulfofMexico, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_GulfofMexico, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_GulfofMexico, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_GulfofMexico, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_GulfofMexico, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

# South Atlantic Region  
``` {r sub_SouthAtlantic, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisSouthAtlanticFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "SouthAtlantic"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_SouthAtlantic, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_SouthAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_SouthAtlantic, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_SouthAtlantic, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_SouthAtlantic, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_SouthAtlantic, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_SouthAtlantic, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_SouthAtlantic, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_SouthAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_SouthAtlantic, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_SouthAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_SouthAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

# Caribbean Region  
``` {r sub_Caribbean, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisCaribbeanFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "Caribbean"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_Caribbean, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_Caribbean, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_Caribbean, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_Caribbean, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_Caribbean, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_Caribbean, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_Caribbean, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_Caribbean, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_Caribbean, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_Caribbean, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_Caribbean, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_Caribbean, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

# Mid-Atlantic Region  
``` {r sub_MidAtlantic, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisMidAtlanticFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "MidAtlantic"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_MidAtlantic, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_MidAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_MidAtlantic, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_MidAtlantic, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_MidAtlantic, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_MidAtlantic, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_MidAtlantic, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_MidAtlantic, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_MidAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_MidAtlantic, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_MidAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_MidAtlantic, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

# NewEngland Region  
``` {r sub_NewEngland, echo=FALSE}
new_tbl <-
  data %>%
  filter(!is.na(MinimumDepthInMeters),
         as.numeric(MinimumDepthInMeters) != 999,
         as.numeric(MinimumDepthInMeters) != -999,
         !is.na(VernacularNameCategory),
         gisNewEnglandFMC == T)

data_flagged<-new_tbl %>%
  filter(Flag == "1")

data_unfl<-new_tbl %>%
  filter(Flag == "0")

x <- "NewEngland"
```

* Total number of records in the region (flagged + unflagged): **`r length(new_tbl$CatalogNumber)`** 

* Total number of unflagged records: **`r length(data_unfl$CatalogNumber)`**  
``` {r FlagProportion_NewEngland, echo=FALSE, results='hide'}
z <- (length(data_flagged$CatalogNumber)/length(new_tbl$CatalogNumber) *100)
```

* Proportion of records that are flagged: **`r format(round(z, 2), nsmall = 2)`%**

* Total number of unique Scientific Names: **`r length(unique(data_unfl$ScientificName))`**

***

##### Table of the number of database records (n) contributed by each Data Provider (`r x`): 
``` {r DataProvider_NewEngland, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(DataProvider) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Pie chart of VernacularNameCategory (`r x`): 
``` {r VerNacularName_Pie_NewEngland, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$VernacularNameCategory, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Taxon Rank (`r x`): 
``` {r TaxonRank_Pie_NewEngland, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$TaxonRank, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.3,
    )
```

***

##### Pie chart of Corals vs. Sponges (`r x`): 
``` {r Coral_v_Sponge_Pie_NewEngland, echo=FALSE, message=FALSE, warning=FALSE}

par(mar=c(0,0,0,0))
par(mgp=c(0, 0, 0))
mytable <- table(data_unfl$Phylum, useNA = "always")
lbls <- paste(names(mytable), "\n", mytable, sep="")
pie(mytable, labels = lbls, cex = 0.8,
    )
```

***

##### Depth distribution of database records (`r x`):
``` {r Depth_Summary_NewEngland, echo=FALSE, message=FALSE, warning=FALSE}
# cut the depth vector and then barplot (varying bins) 
groups = cut(data_unfl$gisDepth, breaks=c(0,50,100,200,500,1000,5000), include.lowest=TRUE)

#bygroup = tapply(data$gisDepth, groups)
table<-table(groups)
table<-as.data.frame(table)
table <- table[rev(order(row.names(table))),]

names.arg = c("0-50","50-100","100-200", "200-500", "500-1000", ">1000")
rev.names.arg= rev(names.arg)

par(mar=c(8,8,4,3))
par(mgp=c(6, 2, 1))

barplot(table$Freq, 
        horiz=T, 
        las=2,
        xlab="Number of Records",
        ylab="Depth in Meters",
        names.arg = rev.names.arg
)
```

***

##### Boxplot of depth by Genus (`r x`):
``` {r Depth_Summary_Boxplots_NewEngland, echo=FALSE, message=FALSE, warning=FALSE,fig.width=12, fig.height=8}
qplot(Genus,as.numeric(DepthInMeters), data=data_unfl, geom=c("boxplot"),alpha=I(1), 
      #main="Depth Distribution of All Taxa in ",
      xlab="Genus", ylab="Depth (meters)") +
theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_y_continuous(limits = c(0, 5000))
```

***

##### Histogram of depth distribution (`r x`):   
``` {r Depth_Histogram_NewEngland, echo=FALSE,fig.width=14, fig.height=8}
# Kernel density plots #
# grouped by X (indicated by color)
qplot(as.numeric(MinimumDepthInMeters), data=data_unfl, geom="histogram", alpha=I(.5), fill = Order,
      xlab="Depth (Meters)", 
      ylab="Number of Database Records", binwidth = 50) +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.05)) +
  scale_x_continuous(limits = c(0, 3500))
```

***

##### Distribution of records by Large Marine Ecosystem designation (`r x`):
``` {r gisLME_NewEngland, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLME) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Cross tablulation of Data Provider by VernacularNameCategory (`r x`): 
``` {r DataProvider-VernacularNameCategory_NewEngland, echo=FALSE}
table <- table(data_unfl$DataProvider,data_unfl$VernacularNameCategory)
table <- kable(table)
table
```

***

##### Ranked list of unique ScientificName (`r x`):
``` {r Ranked_ScientificName_NewEngland, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(ScientificName) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

***

##### Distribution of database records by named gisLocality (`r x`): 
``` {r gisLocality_NewEngland, echo=FALSE}
sum_tbl <-
  data_unfl %>%
  group_by(gisLocality) %>%
  summarize(
    #min.Depth = min(as.numeric(MinimumDepthInMeters)),
    #max.Depth = max(as.numeric(MinimumDepthInMeters)), 
    #mean.Depth = mean(as.numeric(MinimumDepthInMeters)),
    #mean.DepthGIS = mean(as.numeric(gisDepth)),
    n = n()) %>%
  arrange(desc(n))
sum_tbl <- kable(sum_tbl, row.names = F, digits = 2)
sum_tbl
```

